API design for machine learning software: experiences from the scikit-learn project

### 2013-06-25 paper.tex
Fix indentation.
Packages using the scikit-learn conventions.

The simplicity, power, and extensibility of the scikit-learn API is evidenced
by the large and growing user-base, the use of scikit-learn to solve real
problems across a wide array of fields,
as well as the appearance of third-party packages
that follow the scikit-learn conventions and tie into the toolkit.\footnote{
  E.g.\ nolearn, \url{http://pythonhosted.org/nolearn};
  this mention does not imply endorsement of this package.}
While part of the scikit-learn API is necessarily Python-specific,
core concepts may be applicable to
machine learning applications and toolkits
written in other (dynamic) programming languages.

>>>>

While part of the scikit-learn API is necessarily Python-specific,
core concepts may be applicable to
machine learning applications and toolkits
written in other (dynamic) programming languages.
The simplicity, power, and extensibility of the scikit-learn API is evidenced
by the large and growing user-base, the use of scikit-learn to solve real
problems across a wide array of fields,
as well as the appearance of third-party packages
that follow the scikit-learn conventions. Examples of such packages include
\textit{astroML}\footnote{\url{http://astroml.org/}}, a package providing
machine learning tools for astronomers and
\textit{wiseRF}\footnote{\url{http://wise.io}}, a commercial random forest
implementation. The source code of 
the recently-proposed sparse multiclass
algorithm \citep{mblondel-mlj2013}, released as
part of the 
\textit{lightning}\footnote{\url{https://github.com/mblondel/lightning}}
package, also follows the scikit-learn conventions. To maximize ease of use, we
encourage more researchers to follow the scikit-learn conventions when
releasing their software in the future.
